---
title: "2070 Temperature Prediction"
author: "吴千里"
date: "更新于 `r format(Sys.time(), '%d %B, %Y')`"
documentclass: ctexart
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
keywords:
  - 中文
  - R Markdown
output:
  rticles::ctex:
    fig_caption: yes
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

\pagebreak 
# 假设 Assumption
1. 0W-12W（经度）, 54N-70N（纬度）看作能影响鱼群的海域面积  
2. 不考虑未来出现的意外/人为因素  

\pagebreak


# 温度数据
```{r import_data, echo = F}
# import data from datafile
datafileCSV <- read.csv("/Users/qianli/Downloads/datafile.csv")
```

```{r process_data, echo = F}
# 初步处理数据，去掉东经和南纬的数据
library(dplyr)
data <- datafileCSV
# only need West latitude and North longitude
data <- data %>% filter(grepl("W",Longitude) & grepl("N",Latitude))
# Convert each column to numeric data
data[,1] <- as.numeric(substr(data[,1], 1, nchar(data[,1])-1))
data[,2] <- as.numeric(substr(data[,2], 1, nchar(data[,2])-1))
data[,3] <- as.numeric(substr(data[,3], 5,8))
# drop NAs
data <- na.omit(data)
```

```{r set range}
# 设置需要的经纬度范围（可更改）
# Set the bounds of regions here
longitude_lowerbound <- 0
longitude_upperbound <- 12
latitude_lowerbound <- 54
latitude_upperbound <- 70
```

```{r echo = FALSE}
# 提取每年平均温度
# Only require data from 0-12W and 54-70N
data <- data %>% 
  filter(Longitude < longitude_upperbound & 
           Longitude > longitude_lowerbound & 
           Latitude < latitude_upperbound & 
           Latitude > latitude_lowerbound)
```
```{r}
# Get the average temperature for each year
data <- data %>% group_by(Time) %>% summarise(avg_temp = mean(Sea.Surface.Temperature))
# Print data
data
```

\pagebreak

```{r fig.cap="年平均海表温度（0-12W & 54-70N)"}
plot(data$Time, 
     data$avg_temp, 
     col = "blue", 
     main = "Sea Surface Temperature of 0-12W and 54-70N from 1981-2015",
     xlab = "Year", 
     ylab = "Temperature (celsius)")
```

\pagebreak

# 预测区间  

A prediction interval is a type of confidence interval (CI) used with predictions in regression analysis; it is a range of values that predicts the value of a new observation, based on your existing model.  

The formula of prediction interval:
$$\hat{y_h} \pm t_{{\alpha \over 2}, n-2} \cdot \sqrt{MSE(1+{ 1 \over n} + {(x_h - \overline{x})^2 \over \sum(s_i - \overline{x})^2}}$$  

```{r prediction interval, echo=FALSE}
temperature <- data$avg_temp
year <- data$Time
models <- lm(temperature ~ year)
new.year <-  data.frame(
  year = c(2070)
)
```
```{r}
predict(models, newdata = new.year, interval = "prediction")
```

Our 95% Prediction Interval is (8.58, 11.93), which means according to our regression model, the average sea surface temperature in 2070 will fall into the range of 8.58$^\circ$C to 11.93$^\circ$C 95% of time.  

```{r echo = F, fig.cap="2070年的预测区间以及预期数值（红点）", warning=FALSE, message=F}
new.year <- data.frame(
  year = seq(from = 1981, to = 2072, by = 1)
)
pred.int <- predict(models, newdata = new.year, interval = "prediction")
for (i in 36:92) {
  data[i,1] <- data[i-1,1]+1
}
mydata <- cbind(data, pred.int)
library("ggplot2")
p <- ggplot(mydata, aes(Time, avg_temp)) +
  geom_point() +
  stat_smooth(method = lm)


p + geom_line(aes(y = lwr), color = "red", linetype = "dashed")+
    geom_line(aes(y = upr), color = "red", linetype = "dashed")+ theme_bw() +geom_point(x = 2070, y = 10.2526, col = "red")
```





\pagebreak


# (忽略）仅Deterministic的预测
```{r echo = F}
# import temperature data from 1880 - 2020
allTemp <- read.csv("temperature.csv")
allTemp <- allTemp[,c(2,4)]
colnames(allTemp) <- c("Year", "Temperature")
```


```{r echo=F, fig.cap="1880-2020海表温度变化趋势"}
# Plot the scatter plot of temperature and year
plot(allTemp$Year, 
     allTemp$Temperature, 
     xlab = "Year", 
     ylab = "Temperature")
abline(lm(allTemp$Temperature ~ allTemp$Year), col = "red")
```

上图应使用非线性的拟合曲线，或者可以仅使用近50年的数据，如下页面所示：  

\pagebreak
```{r echo=F, fig.cap="1970-2020年海表温度数据拟合曲线"}
plot(allTemp$Year[91:141], 
     allTemp$Temperature[91:141], 
     xlim = c(1970, 2080), 
     ylim = c(-0.2, 2), xlab = "Year", 
     ylab = "Temperature")
abline(lm(allTemp$Temperature[91:141] ~ allTemp$Year[91:141]), col = "red")
points(2070, 1.86, col = "red")
```

上图的\textcolor{red}{红点}代表2070年拟合曲线预测的海水温度，大约为**+1.86** $^\circ$C  

\pagebreak

# 包含Stochasticity的预测  

### 方法一：通过R语言自带公式得出预测区间 
\textcolor{red}{缺点：} 不清楚其统计原理  
\textcolor{green}{优点：} 简单明了，且数据比较合理
```{r}
temperature <- allTemp$Temperature[70:141]
year <- allTemp$Year[70:141]
models <- lm(temperature ~ year)
models
```

```{r}
new.year <-  data.frame(
  year = c(2070)
)
predict(models, newdata = new.year, interval = "prediction")
```

**总结：**预期值是1.56$^\circ$C，预测区间是1.37$^\circ$C - 1.74$^\circ$C。  

\pagebreak

### 方法二：看作discrete model
每年温度变化量是一个取自**1950-2020年温度增加量**的随机数，模拟到2070年  
\textcolor{red}{缺点：} 不确定变成discrete是否合理 + 温度偏高  
\textcolor{green}{优点：} 过程清晰 + 和作业题相似    

```{r echo=F, fig.cap="每年温度变化量的频率分布"}
TempChange <- rep(NA,70)
for (i in 71:140) {
  TempChange[i-70] <- allTemp[i+1,2] - allTemp[i,2]
}
hist(TempChange)
```

```{r background="blue" }
# 1950-2020年间每年温度变化量（后一年温度减前一年）
TempChange
# 上述数据的总结：
summary(TempChange)
# 上述数据的方差： 
sd(TempChange)
```

### predict temperature in 2070 using discrete model
```{r echo=F}
tempPrediction <- function(base = 1.01, x){
  # The temperature of 2020 is 1.01
  temp2020 <- base
  Result <- as.data.frame(matrix(NA, ncol = 2, nrow = 51*x))
  colnames(Result) <- c('Year', 'Temperature')
  
  # loop x times of simulation
  for (j in 1:x) {
    # Create a list to store temperature value
    temp_prediction <- rep(NA, 51)
    temp_prediction[1] <- temp2020
    Result[51*(j-1)+1,1] <- 2020
    Result[51*(j-1)+1,2] <- temp2020
    # let the change of temperature be a random number selected from TempChange to simulate the temperature in 2070
    for (i in 1:50) {
      # randomly select a temperature change
      rand_value <- sample(1:70,1)
      temperature_change <- TempChange[rand_value]
      # Add the temperature change to the temperature of previous year
      temp_prediction[i+1] <- temp_prediction[i]+temperature_change
      Result[51*(j-1)+i+1,1] <- Result[51*(j-1)+i,1]+1
      Result[51*(j-1)+i+1,2] <- temp_prediction[i+1]
    }
  }
  library(ggplot2)
  ggplot(data = Result, aes(x=Year, y=Temperature, group = Year)) + geom_boxplot() + theme_bw()
}

```
```{r fig.cap="50次模拟2070年温度分布"}
# 模拟50次的数据分布
tempPrediction(x = 50)
```

\textcolor{red}{总结：2070年海水表面温度预期值是1.79$^\circ$C， 预测区间为1.7$^\circ$C - 1.9$^\circ$C之间。}  
